---
title: "P8105_HW3_dg3187"
author: "Danyang Gui"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```




### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. 


### Problem 1

```{r}
data("instacart")
```

This dataset contains `r nrow(instacart)` rows and ... columns. 

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day, and order hour. There are also item variables -- name, aisle, department, and some numeric codes. 

How many aisles, and which are most items from?

```{r}
instacart %>% 
	count(aisle) %>% 
	arrange(desc(n))
```


Let's make a plot

```{r}
instacart %>% 
	count(aisle) %>% 
	filter(n > 10000) %>% 
	mutate(
		aisle = factor(aisle),
		aisle = fct_reorder(aisle, n)
	) %>% 
	ggplot(aes(x = aisle, y = n)) + 
	geom_point() + 
	theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


Let's make a table!!

```{r}
instacart %>% 
	filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
	group_by(aisle) %>% 
	count(product_name) %>% 
	mutate(rank = min_rank(desc(n))) %>% 
	filter(rank < 4) %>% 
	arrange(aisle, rank) %>% 
	knitr::kable()
```


Apples vs ice cream..

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```



### Problem 2

Import and clean the data, create a new varible indicating whether the specific day is weekday or weekend.
```{r}
accel_df = 
  read_csv ("./data/accel_data.csv") %>%
  janitor::clean_names() %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute",
    values_to = "count",
    names_prefix = "activity_"
  ) %>%
  mutate(
    day = as.factor(day),
    week = as.factor (week),
    minute = as.numeric(minute),
    count = as.numeric(count),
    weekday_or_weekend = 
      case_when(
        day %in% c("Saturday", "Sunday") ~ "Weekend",
        day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday") ~ "Weekday"))
```
There are `r nrow(accel_df) ` rows and `r ncol(accel_df) ` columns in the existing dataframe now. Variables include `r names(accel_df)`.





```{r}
 accel_df  %>% 
  group_by(week, day) %>% 
  summarize(
    sum_activity_count = sum(count)
  ) %>% 
  pivot_wider(
    names_from = day,
    values_from = sum_activity_count
  ) %>% 
  relocate (week, Monday, Tuesday, Wednesday, Thursday, Friday, Saturday, Sunday) %>%
  knitr::kable(digits = 2) 
```


This produces a 7*5 table. Saturday on week 4 and 5 show exceptionally low activity level. Week 1 Monday was low too.


```{r}
accel_df %>% 
  group_by(week, day_id) %>%
  ggplot(aes(x = minute, y = count, color = day, alpha = .7)) + 
  geom_line() +
  theme(legend.position = "right") +
  stat_smooth(se = F,
              geom ="line"
            ) +
  labs(
    title = "24-hour activity plot",
    x = "Hour",
    y = "Activity Level") + 
  scale_x_continuous(
    breaks = c(0,240, 480, 720, 960, 1200, 1440),
    labels = c("0:00", "4:00", "8:00", "12:00", "16:00", "20:00", "24:00")) + 
  scale_y_continuous(
    trans = "sqrt") +
  viridis::scale_color_viridis(discrete = T, name = "Day")
```

In general, the activity level starts to increase after 6:00 and starts to decrease after 22:00. Friday is kinda special: there's an increase in activity level starting from 20:00.




### Problem 3





